---
title: "Challenge 1 - Team 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Vendex Challenge
## Section A - Group 8
- Luciana
- Matteo Augenti
- Kiko
- Nicolas
- Jose Frank Cuellar

```{r Initialization}
# Clearing workspace
rm(list = ls())

library(tidyverse)

# Read CSV files (transactional is zipped so we use unz())
df_machine <- read.csv('./Data/machine_data.csv')
df_product <- read.csv('./Data/product_data.csv')
df_transactional <- read.csv(unz("./Data/transactional_data.csv.zip", 
                                 'transactional_data.csv'))
```


### **1 General overview of the data:**
#### **a. How many machines are there?**
```{r 1A}
cat('There are', length(df_machine$machine), 'unique machines.')
```

#### **b. What percentage of them are small?**
```{r 1B}
cat(scales::percent(mean(df_machine$small_machine)), 'of the machines are small.')
```

#### **c. How do they distribute in terms of location type i.e. transport, petrol station? Products**
```{r 1C}
plyr::count(df_machine, 'location_type')
```

#### **d. How many products are there?**
```{r 1D1}
cat('There are', length(df_product$product_name), 'unique products.')
```

#### **Which category has the highest number of products?**
```{r 1D2}
head(plyr::count(df_product, 'category'), 1)
```

#### **e. Which category has the highest and lowest average price?**
```{r 1E1}
df_product %>% 
  group_by(category) %>% 
  summarise_at(c('price'), mean) %>% 
  arrange(desc(price))
```
##### *Highest: Milk based 3.42*
##### *Lowest: Sugar candy 2.3*

#### **And within snacks or drinks?**
```{r 1E2}
df_product %>% 
  group_by(type_drink_snack) %>% 
  summarise_at(c('price'), mean) %>% 
  arrange(desc(price))
```

#### **f. Restricting the transactional data to March 2017, what’s the average daily items among small and big machines?**
```{r 1F}
df <- df_transactional %>% 
  filter(lubridate::month(date) == 3)

active_days <- df %>% 
  group_by(machine, date) %>%
  summarise() %>%
  group_by(machine) %>%
  summarise(daysactive = n())

sold_machine <- df %>% 
  group_by(machine) %>%
  summarise(transactions = n())

unique_df <- df %>% 
  group_by(machine) %>% 
  summarise()

unique_machine <- df_machine%>% 
  filter(machine %in% unique_df$machine)

unique_machine$meansold <- sold_machine$transactions / active_days$daysactive

unique_machine %>%
  group_by(small_machine) %>%
  summarise(mean(meansold))
```

#### **Why do you think there is such a difference? Give at least 2 possible reasons.**
##### *Reason 1: Because bigger machines may have more and more varied product that results in more sales*
##### *Reason 2: Because bigger machines are visually more attractive and thus generate more interest/sales*


### **2 Consider the following plot of the number of items sold per machine and day**
```{r 2}
# Find a way to recreate the plot shown in the PDF without merging tables (for practice)
```

#### **Let us focus on the different patterns present in the data:**
#### **a. Is there a general trend in the number of snacks and drinks as the months progress from January to April?**
##### *There seems to be a general trend for both types of products*
#### **Is it the same for snacks and drinks? Why do you think that might be so?**
##### *No, the trend is different with snacks staying roughly about the same throughout those months with a one time minimum items increase during February.*
##### *This might be because the need for snacks is very consistent whereas the need for drinks increases during the warmer months when people tend to be more thirsty (Increased dehydration)*

#### **b. Is there a shorter time period trend as well? Is it the same for snacks and drinks?**
##### *Yes, during Jan - Feb, drinks are at their lowest with a in month down trend*
#### **What do you think might be the cause?**
##### *The cause is likely due to those months often being the coldest during the year and thus there is less need/want for drinks (Less dehydration)*


### **3 Given the following distribution of average income:**
```{r 3}
summary(df_machine$income_average) # Real data does not match provided example, ask about it
```

#### Min.   1st Qu.  Median  Mean    3rd Qu.    Max.       NA's
#### 25540   48860   54100  162900   60960     9777000      97

#### **a) Are there outliers?**
##### *Yes*

#### **How would you treat them?**
##### *I would limit their values to a fixed one - Not sure*

#### **b) Can you give three possibilities on how to treat the NA cases?**
##### *Need to investigate this*
#### **Which option would you choose and why?**
##### *The best one*

##### *Hint: Take a look at the relation between having NA in the income average and the average daily items.*


### **4 According to the following boxplot, what is the median number of hotels in the machine area?**
```{r 4}
boxplot(df_machine$num_hotels, outline = F)
```

#### *According to the boxplot and signaled by the thick black line at the bottom, we can interpret that the median is equal to 0.*


### **5 In this exercise we will build a location score that tells us what’s the average daily items per machine depending on the location it is placed. This model could be used to:**
#### **a) Decide in which locations to place new machines**
#### **b) Construct a benchmark for each machine: how much should it sell according to its location? This can be used to detect problems in machines (i.e. illumination, bad placement within a station etc.)**
#### **For that, you will build a linear model to predict machine daily items using the following features:**
#### **1. Machine size (big or small)**
#### **2. Income of the area**
#### **3. Number of routes in the area**
#### **4. Number of hotels with 4 and 5 stars in the area**
#### **5. 0-1 Indicator of whether the machine has train_AvgDailyPassengers informed, meaning it is a petrol station or other type of location**
```{r 5}
# Some badass code here
```

##### *Hint: You can generate an indicator variable of this sort using the syntax*
##### *dt <- dt %>% mutate(new_column_name = ifelse(is.na(column_name),1,0))*


### **6 Number of other Vendex machines in the area**
#### **Answer the following questions:**
#### **a) Do all variables show statistical significance? Which ones doesn’t? How do you know?**
##### *Hint: Recall that to check the parameters of a glm model called “model1” you need to run summary(model1)*

#### **b) Build another linear model but this time instead of using the variables “total_number_of_routes_600 use the log of that variable in base 10 calling it “log_transport”. Does this new variable show statistical significance?**

#### **Train the model constructed in the previous question (b) removing the variables that do NOT show statistical significance calling it final_model and with that model answer the following questions**

#### **c) How many daily items less do small machines sell all other factors remaining equal?**

#### **d) What’s effect on machine sales does having other nearby machines all other factors remaining equal?**

#### **e) Ranking all machines according to the final_model, what are the real daily sales of the top20% machines with respect to your model prediction? And the real daily sales of the bottom20% machines according to your model? What’s the top20%/bottom20% ratio?**

#### **f) Given the following 2 locations for a big machine:**
#### **1. Supermarket entrance, 2 nearby hotels of 4 stars, 20 transport routes, no nearby machines**
#### **2. Transport station, no nearby hotels of 4 or 5 stars, 10 transport routes nearby, 3 nearby Vendex machines**

#### **Which location would you choose and why?**
##### *I would choose ... because ...*
